Untitled

### 2017-05-29 PlotwithLeaflet.Rmd
LEaflet update
Have managed to make a leaflet doc and save it as an html widget

m <- leaflet(states) %>%
  setView(-96, 37.8, 4) %>%
  addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN')))

```{r}
MyData <- AG %>% filter(grepl("kensington", LAD11NM ,ignore.case = T)) %>%
  mutate(group = lsoa11cd)

MyData <- SpatialPointsDataFrame(coords =MyData[,c(1,2)], data = MyData,
                               proj4string = CRS("+proj=tmerc +lat_0=49 +lon_0=-2 +k=0.9996012717 +x_0=400000 +y_0=-100000 +datum=OSGB36 +units=m +no_defs +ellps=airy +towgs84=446.448,-125.157,542.060,0.1502,0.2470,0.8421,-20.4894"))

#random thing
stuff <-data.frame(lsoa11cd=unique(MyData$lsoa11cd),row.names=unique(MyData$id))

plot(spDF,col=spDF$box_id+1)

m <- leaflet(MyData) %>%
  #setView(-96, 37.8, 4) %>%
  addTiles()

  addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN')))

@@

```{r}
# this code just creates a sample SpatialPointsDataFrame 
x <- c(-10,-10,10,10,-10)
y <- c(-10,10,10,-10,-10)
df.1 <- data.frame(x,y,id=47, order=1:5,hole=F,piece=1,group=47.1,box_id=1)
coordinates(df.1)=c("x","y")
x <- c(+15+3*cos(2*pi/5*(0:5)))
y <- c(-15+3*sin(2*pi/5*(0:5)))
df.2 <- data.frame(x,y,id=48, order=1:6,hole=F,piece=1,group=48.1,box_id=2)
coordinates(df.2)=c("x","y")
x <- c(-15+2*cos(2*pi/8*(0:8)))
y <- c(+15+2*sin(2*pi/8*(0:8)))
df.3.1 <- data.frame(x,y,id=20, order=1:9,hole=F,piece=1,group=20.1,box_id=3)
coordinates(df.3.1)=c("x","y")
x <- c(0+2*cos(2*pi/8*(0:8)))
y <- c(+15+2*sin(2*pi/8*(0:8)))
df.3.2 <- data.frame(x,y,id=20, order=1:9,hole=F,piece=1,group=20.2,box_id=3)
coordinates(df.3.2)=c("x","y")
x <- c(+15+2*cos(2*pi/8*(0:8)))
y <- c(+15+2*sin(2*pi/8*(0:8)))
df.3.3 <- data.frame(x,y,id=20, order=1:9,hole=F,piece=1,group=20.3,box_id=3)
coordinates(df.3.3)=c("x","y")
df <- rbind(df.1,df.2,df.3.1,df.3.2,df.3.3)
df
#              coordinates id order  hole piece group box_id
# 1             (-10, -10) 47     1 FALSE     1  47.1      1
# 2              (-10, 10) 47     2 FALSE     1  47.1      1
# 3               (10, 10) 47     3 FALSE     1  47.1      1
# 4              (10, -10) 47     4 FALSE     1  47.1      1
# 5             (-10, -10) 47     5 FALSE     1  47.1      1
# 6              (18, -15) 48     1 FALSE     1  48.1      2
# 7  (15.92705, -12.14683) 48     2 FALSE     1  48.1      2
# 8  (12.57295, -13.23664) 48     3 FALSE     1  48.1      2
# ...
data <- data.frame(box_id=unique(df$box_id),row.names=unique(df$id))
```

```{r}
points2polygons <- function(df,data) {
  get.grpPoly <- function(group,ID,df) {
         Polygon(coordinates(df[df$id==ID & df$group==group,]))
         }
  get.spPoly  <- function(ID,df) {
         Polygons(lapply(unique(df[df$id==ID,]$group),get.grpPoly,ID,df),ID)
         }
  spPolygons  <- SpatialPolygons(lapply(unique(df$id),get.spPoly,df))
  SpatialPolygonsDataFrame(spPolygons,match.ID=T,data=data)
}

spDF <- points2polygons(df,data)
plot(spDF,col=spDF$box_id+1)

library(rgdal)
writeOGR(spDF,dsn=".",layer="myShapefile", driver="ESRI Shapefile")
```

>>>>

points2polygons <- function(df,data) {
  get.grpPoly <- function(group,ID,df) {
         Polygon(coordinates(df[df$id==ID & df$group==group,]))
         }
  get.spPoly  <- function(ID,df) {
         Polygons(lapply(unique(df[df$id==ID,]$group),get.grpPoly,ID,df),ID)
         }
  spPolygons  <- SpatialPolygons(lapply(unique(df$id),get.spPoly,df))
  SpatialPolygonsDataFrame(spPolygons,match.ID=T,data=data)
}

m <- leaflet(states) %>%
  #setView(-96, 37.8, 4) %>%
  addTiles()
  # addProviderTiles("MapBox", options = providerTileOptions(
  #   id = "mapbox.light",
  #   accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN')))

@@

```{r}
MyData <- AG %>% filter(grepl("kensington", LAD11NM ,ignore.case = T)) %>%
  rename(LSOA_CODE = lsoa11cd)

MyData <- SpatialPointsDataFrame(coords =MyData[,c(1,2)], data = MyData,
                               proj4string = CRS('+proj=tmerc +lat_0=49 +lon_0=-2 +k=0.9996012717 +x_0=400000 +y_0=-100000 +ellps=airy +datum=OSGB36 +units=m +no_defs'))
MyData <- spTransform(MyData, CRS("+init=epsg:4326"))
#random thing
stuff <-data.frame(LSOA_CODE=unique(MyData$LSOA_CODE),row.names=unique(MyData$id))

AG2 <- AG %>% group_by(LSOA_CODE) %>% summarise_all(funs(first))

MyData <- merge(MyData, Chelseainfo)

v<-"pk.eyJ1Ijoiam9ubm9iIiwiYSI6ImNqM2FlNXhpbDAwM3gzMW83ZW1hbHI0bzYifQ.4AfaY0Un0bKU41hZscpy9Q"

m <- leaflet(MyData) %>%
    #addTiles()
    addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = v))

bins <- c(0, 10, 20, 25, 100)
pal <- colorBin("YlOrRd", domain = MyData$LowUsePerc, bins = bins)

labels <- sprintf(
  "<strong>%s</strong><br/>Low-use  %g &#37",
  MyData$WD16NM, MyData$LowUsePerc
) %>% lapply(htmltools::HTML)

z <-m %>% addPolygons(
  fillColor = ~pal(LowUsePerc),
  weight = 2,
  opacity = 1,
  color = "white",
  dashArray = "3",
  fillOpacity = 0.7,
  highlight = highlightOptions(
    weight = 5,
    color = "#666",
    dashArray = "",
    fillOpacity = 0.7,
    bringToFront = TRUE),
  label = labels,
  labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "15px",
    direction = "auto")) %>%
  addLegend(pal = pal, values = ~density, opacity = 0.7, title = NULL,
    position = "bottomright")

saveWidget(z, file="m.html" )

mapshot(z, url = paste0(getwd(), "/map.html"))
```
